=
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Remember, we are interested in predicting the likelihood of an individual supporting
a policy based on the number of countries participating and the possible sanctions for
non-compliance.
Fit an additive model. Provide the summary output, the global null hypothesis,
and p-value. Please describe the results and provide a conclusion.

##1. Fit an Additive Model
```{r}
# Load the data at first, and because of the data type, I use the load function
load("climateSupport.RData")

# Fit an additive model with the data I loaded
model <- glm(choice ~ countries + sanctions, data = climateSupport, family = binomial())

# Display the summary of the model to get the coefficients, global null hypothesis, and p-value
summary(model)
```

##2. Analysis Based on the Model
(a) Change in Odds for Increasing Sanctions
You would extract the coefficients for sanctions from your model and calculate the odds ratio for the change from 5% to 15%.
```{r}
# I use a simple way to calculate for that instead of using some function because there are some system error in my Rstudio when I finish the homework

# Calculate predicted probability for sanctions at 5%
prob_5 <- predict(model, newdata = data.frame(countries = "160 of 192", sanctions = "5%"), type = "response")

# Calculate predicted probability for sanctions at 15%
prob_15 <- predict(model, newdata = data.frame(countries = "160 of 192", sanctions = "15%"), type = "response")

# Calculate odds
odds_5 <- prob_5 / (1 - prob_5)
odds_15 <- prob_15 / (1 - prob_15)

# Calculate odds ratio
odds_ratio <- odds_15 / odds_5

print(odds_ratio)
```
```{r}
# Calculate the predicted probability of support with 5% sanctions under 20 of 192 country participation
prob_5 <- predict(model, newdata = data.frame(countries = "20 of 192", sanctions = "5%"), type = "response")

# Calculate the predicted probability of support with 15% sanctions under 20 of 192 country participation
prob_15 <- predict(model, newdata = data.frame(countries = "20 of 192", sanctions = "15%"), type = "response")

# Calculate odds for both levels of sanctions
odds_5 <- prob_5 / (1 - prob_5)
odds_15 <- prob_15 / (1 - prob_15)

# Calculate odds ratio to assess the impact of increasing sanctions on the odds of supporting the policy
odds_ratio <- odds_15 / odds_5

# Print the odds ratio
print(odds_ratio)
```


(b) Estimate Probability with Specific Conditions
To estimate the probability, you'll use the model coefficients and apply them to the specific scenario.
```{r}

# Calculate estimated probability
prob <- predict(model, newdata = data.frame(countries = "80 of 192", sanctions = "None"), type = "response")

print(prob)
```
(c) Test for Interaction
To test for interaction, you would fit another model including an interaction term and compare it with the original model.

```{r}
# Fit model with interaction
model_interaction <- glm(choice ~ countries * sanctions, data = climateSupport, family = binomial())

# Compare models
anova(model, model_interaction, test = "Chisq")
```
