---
output:
  pdf_document: default
  html_document: default
date: "2024-01-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```


## Question 1



The Kolmogorov-Smirnov test uses cumulative distribution statistics test the similarity of the empirical distribution of some observed data and a specified PDF, and serves as a goodness of fit test. The test statistic is created by: 


$$
D=\max _{i=1: n}\left\{\frac{i}{n}-F_{(i)}, F_{(i)}-\frac{i-1}{n}\right\}
$$



where  $F$  is the theoretical cumulative distribution of the distribution being tested and  $F_{(i)}$  is the  i  th ordered value. Intuitively, the statistic takes the largest absolute difference between the two distribution functions across all  x  values. Large values indicate dissimilarity and the rejection of the hypothesis that the empirical distribution matches the queried theoretical distribution. The p-value is calculated from the Kolmogorov- Smirnoff CDF:

$$
p(D \leq x) \frac{\sqrt{2 \pi}}{x} \sum_{k=1}^{\infty} e^{-(2 k-1)^{2} \pi^{2} /\left(8 x^{2}\right)}
$$



which generally requires approximation methods (see Marsaglia, Tsang, and Wang 2003).
This so-called non-parametric test (this label comes from the fact that the distribution of
the test statistic does not depend on the distribution of the data being tested) performs



poorly in small samples, but works well in a simulation environment. Write an R function
that implements this test where the reference distribution is normal. Using R generate 1,000
Cauchy random variables (rcauchy(1000, location = 0, scale = 1)) and perform the
test (remember, use the same seed, something like set.seed(123), whenever you’re generating your own data).






```{r}
ks_test_normal <- function(observed_data, seed = 123) {
  set.seed(seed)
  
  # Generate Cauchy random variables
  cauchy_data <- rcauchy(1000, location = 0, scale = 1)
  
  ECDF <- ecdf(observed_data)
  empirical_CDF <- ECDF(observed_data)
  
  theoretical_CDF <- pnorm(observed_data)
  
  # Calculate test statistic
  D <- max(abs(empirical_CDF - theoretical_CDF))
  
  # Calculate p-value using Kolmogorov-Smirnov CDF
  p_value <- sqrt(2 * pi) / D * sum(exp(-(2 * (1:1000) - 1)^2 * pi^2 / (8 * D^2)))
  
  # Return the test statistic and p-value
  return(list(test_statistic = D, p_value = p_value))
}

# Example usage:
observed_data <- rcauchy(1000, location = 0, scale = 1)
result <- ks_test_normal(observed_data, seed = 123)
print(result)
```

This function, `ks_test_normal`, takes observed data as input, generates Cauchy random variables, computes the empirical distribution, and then calculates the test statistic and p-value. Note that the p-value calculation involves an infinite sum, so it might require numerical approximation methods. The provided code uses a finite sum for demonstration purposes, and you may want to explore more accurate methods if needed.




##  Question 2



Estimate an OLS regression in R that uses the Newton-Raphson algorithm (specifically BFGS,
which is a quasi-Newton method), and show that you get the equivalent results to using lm.
Use the code below to create your data.




```{r}
# Set the random seed for reproducibility
set.seed(123)

# Create a data frame with two columns, where 'x' is generated from a uniform distribution in the range [1, 10],
# and 'y' is generated based on a linear relationship with added noise
data <- data.frame(x = runif(200, 1, 10))
data$y <- 0 + 2.75 * data$x + rnorm(200, 0, 1.5)

# Define the objective function for ordinary least squares (OLS)
ols_obj_function <- function(beta, x, y) {
  y_pred <- beta[1] + beta[2] * x
  residuals <- y - y_pred
  sum(residuals^2)
}

# Use the BFGS optimization algorithm to fit the model with initial parameters set to c(0, 1)
result_optim <- optim(par = c(0, 1), fn = ols_obj_function, x = data$x, y = data$y, method = "BFGS")

# Get the parameter estimates from the optimization results
coef_optim <- result_optim$par

# Fit a linear model using the lm function, y ~ x
model_lm <- lm(y ~ x, data = data)

# Get the parameter estimates from the lm function
coef_lm <- coef(model_lm)

# Print the coefficients obtained using the BFGS optimization algorithm
cat("Coefficients using BFGS optimization:\n")
print(coef_optim)

# Print the coefficients obtained using the lm function
cat("\nCoefficients using lm function:\n")
print(coef_lm)
```

This code defines an objective function `ols_obj_function` that computes the sum of squared residuals for given coefficients. The `optim` function is then used to minimize this objective function with the BFGS algorithm. The results are compared with the `lm` function.

Make sure you have the BFGS algorithm available in your R environment. If not, you might need to install the `stats` package, which typically includes BFGS.